A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-10 4_method.tex
lil fixes
reformulated mathematical requirements on strategy

The following restrictions hold:
\begin{itemize}
\item $tb(d) \geq 0, W(n,d) > 0, L(n, d) \geq 0$
\item $120\degree < \alpha_{\text{max}} \leq 180\degree$
\item $W$ is symetric: $W(n, d)_i = W(n, d)_{n-i-1}$
\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
\item $b^{-1}(n) < p(n) < b^{-1}(n + 1)$
%\item $b \left( p(n) \right) = n$ % follows from the above!
\item $b(d)$ is monotonic: $ b(d) \leq b(d + \epsilon)$
\item the width $W(c, d)_n$ of each bead $n$ increases monotonically and gradually in regions with constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
\end{itemize}

The angle requirement ansures that there is never a 3-way junction of significant bones.

@@

\subsubsection{Proposed optimal beading strategy}
\todo{This section is about some optimal strategy which hasn't been fully developed (yet?).}

\todo{This section still formules the beading strategy in terms of radius instead of diameter, which halves the $n$ values.}

@@

i

>>>>

The following restrictions hold:
\begin{itemize}
\item $b(d) \geq 0, W(n,d) > 0, L(n, d) \geq 0, t \geq 0$
\item $120\degree < \alpha_{\text{max}} \leq 180\degree$
\item $W$ is symetric: $W(n, d)_i = W(n, d)_{n-i-1}$
\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
\item $p$ is within the range of optimal: $b^{-1}(n) < p(n) < b^{-1}(n + 1)$
%\item $b \left( p(n) \right) = n$ % follows from the above!
\item $b$ is monotonic: $ b(d) \leq b(d + \epsilon)$
\item $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
\item $t$ is viable: $\forall i \in \mathbb{N} : t < \left( p(i + 1) - p(i) \right) /{2 \cos \alpha_\text{max}}$
\end{itemize}

The angle requirement ensures that there is never a 3-way junction of significant bones.

@@

\subsubsection{Proposed optimal beading strategy}
@Readers: you can skip reading this section for now.
\todo{This section is about some optimal strategy which hasn't been fully developed (yet?).}
\todo{This section still formules the beading strategy in terms of radius instead of diameter, which halves the $n$ values.}

@@
